#FUNGuild analyses

# Libraries

```{r}

library(plotrix)
library(patchwork)

```
# Plant Pathogen

only FF-Q had 1 plant pathogen
This was the only one that was confident it was a plant pathogen
There were other samples that could possibly be other things as well

``` {r}
head(dat7)
dat7$plantpathogenpercent<-dat7$plantpathogen/dat7$totalabundance*100
dat7$plantpathogentaxapercent<-dat7$plantpathogentaxa/dat7$SR*100
dat7$plantpathogenbroadpercent<-dat7$plantpathogenbroad/dat7$totalabundance*100
dat7$plantpathogenbroadprobablehppercent<-dat7$plantpathogenbroadprobablehp/dat7$totalabundance*100
dat7$symbiotrophpercent<-dat7$symbiotroph/dat7$totalabundance*100
dat7$plantpathogenbroadprobablehptaxapercent<-dat7$plantpathogenbroadprobablehptaxa/dat7$SR*100
dat7$symbiotrophtaxapercent<-dat7$symbiotrophtaxa/dat7$SR*100
dat7$symbiotrophprobablehptaxapercent<-dat7$symbiotrophprobablehp/dat7$SR*100

options(contrasts=c("contr.helmert","contr.poly"))


pathmean<-dat7%>%
  group_by(Community.x,Site)%>%
    mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))%>%
  summarise(mean=mean(plantpathogentaxapercent),se=std.error(plantpathogentaxapercent),count=n())

#pdf("/Users/farrer/Dropbox/EmilyComputerBackup/Documents/LAmarsh/Culturing/Manuscripts/richness.pdf",width=6.6,height=3.5)
funp <- ggplot(pathmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="Pathogen") +
  theme_classic()+
  theme(line=element_line(size=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) +
  facet_wrap(vars(Site),strip.position = "bottom")
#dev.off()

pathmean<-dat7%>%
  group_by(Community.x)%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))%>%
  summarise(mean=mean(plantpathogentaxapercent),se=std.error(plantpathogentaxapercent),count=n())

funp2 <- ggplot(pathmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) 

```

# Ericoid Mycorrhizal

``` {r}
head(dat7)
dat7$ericoidpercent<-dat7$ericoid/dat7$totalabundance*100
dat7$ericoidtaxapercent<-dat7$ericoidtaxa/dat7$SR*100
dat7$ericoidbroadpercent<-dat7$ericoidbroad/dat7$totalabundance*100
dat7$ericoidbroadprobablehppercent<-dat7$ericoidbroadprobablehp/dat7$totalabundance*100
dat7$ericoidbroadprobablehptaxapercent<-dat7$ericoidbroadprobablehptaxa/dat7$SR*100

options(contrasts=c("contr.helmert","contr.poly"))


pathmean<-dat7%>%
  group_by(Community.x,Site)%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))%>%
  summarise(mean=mean(ericoidtaxapercent),se=std.error(ericoidtaxapercent),count=n())

#pdf("/Users/farrer/Dropbox/EmilyComputerBackup/Documents/LAmarsh/Culturing/Manuscripts/richness.pdf",width=6.6,height=3.5)
funer <- ggplot(pathmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="Ericoid Mycorrhizal") +
  theme_classic()+
  theme(line=element_line(size=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) +
  facet_wrap(vars(Site),strip.position = "bottom")
#dev.off()

pathmean<-dat7%>%
  group_by(Community.x)%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))%>%
  summarise(mean=mean(ericoidtaxapercent),se=std.error(ericoidtaxapercent),count=n())

funer2 <- ggplot(pathmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) 

```
# Symbiotroph

```{r}

pathmean<-dat7%>%
  group_by(Community.x,Site)%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))%>%
  summarise(mean=mean(symbiotrophtaxapercent),se=std.error(symbiotrophtaxapercent),count=n())

#pdf("/Users/farrer/Dropbox/EmilyComputerBackup/Documents/LAmarsh/Culturing/Manuscripts/richness.pdf",width=6.6,height=3.5)
funsym <- ggplot(pathmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="Symbiotroph") +
  theme_classic()+
  theme(line=element_line(size=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) +
  facet_wrap(vars(Site),strip.position = "bottom")
#dev.off()

pathmean<-dat7%>%
  group_by(Community.x)%>%
    mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))%>%
  summarise(mean=mean(symbiotrophtaxapercent),se=std.error(symbiotrophtaxapercent),count=n())

funsym2 <- ggplot(pathmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1)

```
# Saprotroph

```{r}

head(dat7)
dat7$saprotrophpercent<-dat7$saprotroph/dat7$totalabundance*100
dat7$saprotrophtaxapercent<-dat7$saprotrophtaxa/dat7$SR*100
dat7$saprotrophbroadpercent<-dat7$saprotrophbroad/dat7$totalabundance*100
dat7$saprotrophbroadprobablehppercent<-dat7$saprotrophbroadprobablehp/dat7$totalabundance*100
dat7$saprotrophbroadprobablehptaxapercent<-dat7$saprotrophbroadprobablehptaxa/dat7$SR*100

options(contrasts=c("contr.helmert","contr.poly"))


pathmean<-dat7%>%
  group_by(Community.x,Site)%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))%>%
  summarise(mean=mean(saprotrophtaxapercent),se=std.error(saprotrophtaxapercent),count=n())

#pdf("/Users/farrer/Dropbox/EmilyComputerBackup/Documents/LAmarsh/Culturing/Manuscripts/richness.pdf",width=6.6,height=3.5)
funsap <- ggplot(pathmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="Saprotroph") +
  theme_classic()+
  theme(line=element_line(size=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) +
  facet_wrap(vars(Site),strip.position = "bottom")
#dev.off()

pathmean<-dat7%>%
  group_by(Community.x)%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))%>%
  summarise(mean=mean(saprotrophtaxapercent),se=std.error(saprotrophtaxapercent),count=n())

funsap2 <- ggplot(pathmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) 


```
# Large funguild figure

```{r}

# all plots together using the patchwork package
funall <- (funp | funp2) / (funer | funer2)
funall <- funall + plot_annotation(
  title = 'Average Percentage',
  theme = theme(plot.title = element_text(hjust = 0.5)))

funall2 <- (funsym | funsym2) / (funsap | funsap2)

```


## Stats

```{r}
m1p<-lme(plantpathogentaxapercent~Community.x+Site,random=~1|PlantIndividual,data=dat7,na.action=na.omit)
anova(m1p,type="marginal")
hist(resid(m1p))
boxplot(resid(m1p)~dat7$CommunitySitePL)

m2p<-lme(plantpathogentaxapercent~Community.x*Site,random=~1|PlantIndividual,data=dat7,na.action=na.omit)
anova(m2p,type="marginal")

m1e<-lme(ericoidtaxapercent~Community.x+Site,random=~1|PlantIndividual,data=dat7,na.action=na.omit)
anova(m1e,type="marginal")
hist(resid(m1e))
boxplot(resid(m1e)~dat7$CommunitySitePL)

m2e<-lme(ericoidtaxapercent~Community.x*Site,random=~1|PlantIndividual,data=dat7,na.action=na.omit)
anova(m2e,type="marginal")

m1sym<-lme(symbiotrophtaxapercent~Community.x+Site,random=~1|PlantIndividual,data=dat7,na.action=na.omit)
anova(m1sym,type="marginal")
hist(resid(m1sym))
boxplot(resid(m1sym)~dat7$CommunitySitePL)

m2sym<-lme(symbiotrophtaxapercent~Community.x*Site,random=~1|PlantIndividual,data=dat7,na.action=na.omit)
anova(m2sym,type="marginal")

m1sap<-lme(saprotrophtaxapercent~Community.x+Site,random=~1|PlantIndividual,data=dat7,na.action=na.omit)
anova(m1sap,type="marginal")
hist(resid(m1sap))
boxplot(resid(m1sap)~dat7$CommunitySitePL)

m2sap<-lme(saprotrophtaxapercent~Community.x*Site,random=~1|PlantIndividual,data=dat7,na.action=na.omit)
anova(m2sap,type="marginal")

```

# Pie charts by species
this didn't seem very useful so I discontinued
get the full list of taxa from each species, and make a pie chart

```{r}
otulist<-dat7%>%
  group_by(Community.x)%>%
  summarise(across(OTU0:OTU9,sum))

ind<-which(guilds2$guild=="Plant Pathogen")
pathos<-guilds2[ind,]$OTU

DM<-colnames(otulist)[which(otulist[1,]>0)]
DM2<-length(which(pathos%in%DM))
DM3<-length(DM)
pie(c(DM2/DM3,1-DM2/DM3),col=c("black","green"))

SB<-colnames(otulist)[which(otulist[2,]>0)]
SB2<-length(which(pathos%in%SB))
SB3<-length(SB)
pie(c(SB2/SB3,1-SB2/SB3),col=c("black","green"))

```