#Libraries

```{r}

library(cba)
library(remotes)
#remotes::install_github("jfq3/QsRutils")
library(QsRutils)
library(patchwork)
library(forcats)
library(picante)
library(cowplot)
library(agricolae)
library(tidyr)
library(car)
library(ggplot2)
library(dplyr)

```
# ANOVA Helmert

```{r}

options(contrasts=c("contr.helmert","contr.poly"))

```

#Ordination 

calculating MDP (mean pairwise distance) matrix for use in ordination

Bray-Curtis dissimilarity: The difference in richness and abundance across environments (samples). Weight on abundance. Measures the differences from 0 (equal communities) to 1 (different communities)
Jaccard distance: Based on the presence/absence of species (diversity). It goes from 0 (same species in the community) to 1 (no species in common)
UniFrac: Measures the phylogenetic distance; how alike the trees in each community are. There are two types, without weights (diversity) and with weights (diversity and abundance)

```{r}


datp@sam_data[["Community.x"]] <-  fct_relevel(datp@sam_data[["Community.x"]],"SB", "MM", "DM", "FF")

MPDdist<-comdist(data.frame(t(otu_table(datp))), cophenetic(phy_tree(datp)), abundance.weighted=F)
MPDdistweighted<-comdist(data.frame(t(otu_table(datp))), cophenetic(phy_tree(datp)), abundance.weighted=T)

#cleanedtree_v2 <- read.tree("C:/Users/Kacey/Documents/Tulane/Lab/Culture/Geum roots/Data/cleanedtree_V2.nwk")

cleanedtree_v2 <- read.tree("cleanedtree_V2.nwk")

cleanedtree_v2$tip.label <- geumroot[[16]][match(cleanedtree_v2$tip.label, geumroot[[1]])]

#unifracp<-unifrac(otus,tree) #doesnt work with subsetting b/c sample names are not the same
unifracp<-unifrac(t(otu_table(datp)),cleanedtree_v2)

```

# all

```{r}
datp
MPDdist #(unweighted)
MPDdistweighted

#take out singletons. 
datp2<-datp%>%
  filter_taxa(function(x) sum(x>0) >1, prune=T)
datp3<-prune_samples(sample_sums(datp2)>=1, datp2)

```

#Stats for composition

```{r}
#bray curtis
#mynmdsALLb <- ordinate(datp3, "CAP",distance(datp3, method = "bray", binary = F),formula=as.formula(~Community.x+Site+Condition(PlantIndividual)))
#anova(mynmdsALLb,by="margin",permutations = how(nperm=9999))

library("phyloseq")
mynmdsALLb <- ordinate(datp3, "CAP",distance(datp3, method = "bray", binary = F),formula=as.formula(~Community.x+Site))
anova(mynmdsALLb,by="margin")
#mynmdsALLb <- ordinate(datp3, "CAP",distance(datp3, method = "bray", binary = F),formula=as.formula(~Community.x*Site))
#anova(mynmdsALLb,by="margin")

#Getting variance explained
m1<-ordinate(datp3, "CAP",distance(datp3, method = "bray", binary = F),formula=as.formula(~Community.x+Condition(PlantIndividual+Site)))
summary(m1)
m1<-ordinate(datp3, "CAP",distance(datp3, method = "bray", binary = F),formula=as.formula(~Site+Condition(PlantIndividual+Community.x)))
summary(m1)

```


#use one of these for ms

```{r}

ord <- plot_ordination(datp3, mynmdsALLb, type="samples", color="Site",shape="Community.x",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  scale_shape_manual(values=c(16,3,15,17,5))+ 
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(x=CAP1,y=CAP2,fill=Site),level=.95,inherit.aes = F)

plot1<-plot_ordination(datp3, mynmdsALLb, type="samples", color="Community.x",shape="Site",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  scale_shape_manual(values=c(5,3,16,15,17))+ 
  geom_point(size = 2)+
  #stat_ellipse(geom = "polygon", type="t", alpha=0, aes(x=CAP1,y=CAP2,color=Site),level=.95,inherit.aes = F)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(x=CAP1,y=CAP2,fill=Community.x),level=.95,inherit.aes = F)

#Plotting convex hulls rather than ellipses, USE THIS FOR MANUSCRIPT
site_scores1 <- data.frame(cbind(sample_data(datp3),vegan::scores(mynmdsALLb)$sites,labels=rownames(vegan::scores(mynmdsALLb)$sites)))

hull1 <- site_scores1 %>%
  group_by(Community.x) %>%
  slice(chull(CAP1,CAP2))

#kacey use this one
plot1<-ggplot(site_scores1)+
  theme_classic()+
  theme(legend.position = "none")+
  xlab("CAP1 [7.7%]") +  # 
  ylab("CAP2 [3.6%]") +  # 
  annotate("text",x=1.5,y=3.1,label="Community *\nSite         NS")+
  expand_limits(x=2.5,y = 3.4)+
  scale_shape_manual(values=c(5,3,16))+ 
  geom_point(aes(x=CAP1, y=CAP2,color=Community.x,shape=Site),size = 2)+
  geom_polygon(data=hull1,aes(x=CAP1,y=CAP2, fill=Community.x,colour = Community.x),alpha=.2)

# p1=plot_ordination(datp3, mynmdsALLb, type="samples",shape="HostPlant",color="HostPlant",axes=c(1,2))
# 
# ggplot(p1$data, aes(x=CAP1,y=CAP2,color="HostPlant",shape="HostPlant")) +
#   stat_ellipse(data=test,geom = "polygon", type="t", alpha=0.2, aes(fill=Site),level=.95)+
#   geom_point(data=test)
# 
# test<-plot_ordination(datp3, mynmdsALLb, type="samples",color=NULL,shape=NULL,axes=c(1,2),justDF = T)

```  


#Stats for MPD ordination

```{r}

#MPD
#mynmdsALLm <- ordinate(datp, "CAP",distance=MPDdistweighted,formula=as.formula(~Community.x+Site+Condition(PlantIndividual)))
#mynmdsALLm <- ordinate(datp, "CAP",distance=MPDdistweighted,formula=as.formula(~HostPlant+Site))
mynmdsALLm <- ordinate(datp, "CAP",distance=MPDdistweighted,formula=as.formula(~Community.x+Site))
anova(mynmdsALLm,by="margin")
mynmdsALLm <- ordinate(datp, "CAP",distance=MPDdistweighted,formula=as.formula(~Community.x*Site))
anova(mynmdsALLm,by="margin")
#anova(mynmdsALLm,by="margin",permutations = how(blocks=sample_data(datp)$Year,nperm=9999)) #adding permutations within year does not change the anova results

#percent explained
m1 <- ordinate(datp, "CAP",distance=MPDdistweighted,formula=as.formula(~Community.x+Condition(PlantIndividual+Site)))
summary(m1)
m1 <- ordinate(datp, "CAP",distance=MPDdistweighted,formula=as.formula(~Site+Condition(PlantIndividual+Community.x)))
summary(m1)

```

#Ordination plot

```{r}

plot2<-plot_ordination(datp, mynmdsALLm, type="samples", color="Community.x",shape="Site",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  scale_shape_manual(values=c(5,3,16,15,17))+ 
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(x=CAP1,y=CAP2,fill=Community.x),level=.95,inherit.aes = F)

#with edges on the ellipse
plot3 <- plot_ordination(datp, mynmdsALLm, type="samples", color="Community.x",shape="Site",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  scale_shape_manual(values=c(5,3,16,15,17))+ 
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(x=CAP1,y=CAP2,fill=Community.x, color=Community.x),level=.95,inherit.aes = F)

plot4 <- plot_ordination(datp, mynmdsALLm, type="samples", color="Community.x",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(fill=Community.x),level=.95)

#Using convex hulls USE THIS FOR MS
site_scores2 <- data.frame(cbind(sample_data(datp),vegan::scores(mynmdsALLm)$sites,labels=rownames(vegan::scores(mynmdsALLm)$sites)))

hull2 <- site_scores2 %>%
  group_by(Community.x) %>%
  slice(chull(CAP1,CAP2))

levels(site_scores2$Site) <- c("Soddie", "Saddle")
colnames(site_scores2)[2] <- "Community"
colnames(hull2)[2] <- "Community"

#Kacey use this one
plot2<-ggplot(site_scores2)+
  theme_classic()+#  theme(legend.position = "none")
  xlab("CAP1 [5.8%]") +  # 
  ylab("CAP2 [3.6%]") +  # 
  annotate("text",x=1.4,y=2.5,label="Community \u2020\nSite        NS")+
  expand_limits(x = 2.3, y = 2.7)+
  scale_shape_manual(values=c(5,3,16))+ 
  geom_point(aes(x=CAP1, y=CAP2,color=Community,shape=Site),size = 2)+
  geom_polygon(data=hull2,aes(x=CAP1,y=CAP2, fill=Community,colour = Community),alpha=.2)

#jaccard
mynmdsALLj <- ordinate(datp, "CAP",distance(datp, method = "jaccard", binary = TRUE),formula=as.formula(~Community.x+Site+Condition(PlantIndividual)))
anova(mynmdsALLj,by="margin",permutations = how(nperm=9999))

plot5 <- plot_ordination(datp, mynmdsALLj, type="samples", color="Site",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(fill=Site),level=.95)

# figure for comp and mdp using bray-curtis dissimilarity for beta diveristy
#pdf("/Users/farrer/Dropbox/EmilyComputerBackup/Documents/LAmarsh/Culturing/Manuscripts/ordinationcompmpdhulls.pdf",height = 3.5,width = 11)
ord2 <- plot_grid(plot1, plot2, nrow = 1, labels=c("A. Composition","B. MPD"),label_fontface = "plain",hjust=c(-.4,-0.8),vjust=1,rel_widths = c(1.4,2))
#dev.off()

```

# By Site
Does host plant affect composition within each site?
blocks=sample_data(datpTC)$HostPlant

```{r}

#P = Soddie

datpP<-datp%>%
  subset_samples(Site=="P")%>%
  filter_taxa(function(x) sum(x>0) >0, prune=T)
unifracP<-subset_dist(datpP, unifracp)
MPDdistP<-subset_dist(datpP, MPDdist)

mynmdsPj <- ordinate(datpP, "CAP",distance(datpP, method = "jaccard", binary = TRUE),formula=as.formula(~Community.x+Condition(PlantIndividual)))
anova(mynmdsPj,by="margin",permutations = how(nperm=9999))

mynmdsPu <- ordinate(datpP, "CAP",distance=unifracP,formula=as.formula(~Community.x+Condition(PlantIndividual)))
anova(mynmdsPu,by="terms",permutations = how(nperm=9999))

mynmdsPm <- ordinate(datpP, "CAP",distance=MPDdistP,formula=as.formula(~Community.x))
anova(mynmdsPm,by="terms",permutations = how(nperm=9999))

ordP <- plot_ordination(datpP, mynmdsPm, type="samples", color="Community.x",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  geom_point(size = 2)+
  #scale_color_manual(values = c("#0047b3", "#99c2ff","#2d862d","#79d279","#b30000","#ff8080"),labels = c("Fresh Native", "Fresh Phragmites","Brackish Native","Brackish Phragmites","Saline Native","Saline Phragmites"),name = "Marsh class/Invasion")+
  #scale_fill_manual(values = c("#0047b3", "#99c2ff","#2d862d","#79d279","#b30000","#ff8080"),labels = c("Fresh Native", "Fresh Phragmites","Brackish Native","Brackish Phragmites","Saline Native","Saline Phragmites"),name = "Marsh class/Invasion")+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(fill=Community.x),level=.95)


#Q = Saddle

datpQ<-datp%>%
  subset_samples(Site=="Q")%>%
  filter_taxa(function(x) sum(x>0) >0, prune=T)
unifracQ<-subset_dist(datpQ, unifracp)
MPDdistQ<-subset_dist(datpQ, MPDdist)

mynmdsQj <- ordinate(datpQ, "CAP",distance(datpQ, method = "jaccard", binary = TRUE),formula=as.formula(~Community.x+Condition(PlantIndividual)))
anova(mynmdsQj,by="terms",permutations = how(nperm=9999))

mynmdsQu <- ordinate(datpQ, "CAP",distance=unifracQ,formula=as.formula(~Community.x+Condition(PlantIndividual)))
anova(mynmdsQu,by="terms",permutations = how(nperm=9999))#

mynmdsQm <- ordinate(datpQ, "CAP",distance=MPDdistQ,formula=as.formula(~Community.x+Condition(PlantIndividual)))
anova(mynmdsQm,by="terms",permutations = how(nperm=9999))

ordQ <- plot_ordination(datpQ, mynmdsQm, type="samples", color="Community.x",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(fill=Community.x),level=.95)

```



# By Plant Community
Does site affect composition within each site?

plots show x as cap1 and y as mds1
CAP1
The constrained axis, which corresponds to variance in community composition that is explained by a conditioning variable.
MDS1
The unconstrained axis, which corresponds to variance in community composition that is not explained by a conditioning variable.
CAP canonical analysis of principal coordinates, MDS multidimensional scaling

```{r}
#SB 

datpSB<-datp%>%
  subset_samples(Community.x=="SB")%>%
  filter_taxa(function(x) sum(x>0) >0, prune=T)
unifracSB<-subset_dist(datpSB, unifracp)
MPDdistSB<-subset_dist(datpSB, MPDdist)

#jaccard
mynmdsSBj <- ordinate(datpSB, "CAP",distance(datpSB, method = "jaccard", binary = TRUE),formula=as.formula(~Site+Condition(PlantIndividual)))
anova(mynmdsSBj,by="terms",permutations = how(nperm=9999))

#unifrac
mynmdsSBu <- ordinate(datpSB, "CAP",distance=unifracSB,formula=as.formula(~Site+Condition(PlantIndividual)))#
anova(mynmdsSBu,by="terms",permutations = how(nperm=9999))

#bray-curtis
mynmdsSBm <- ordinate(datpSB, "CAP",distance=MPDdistSB,formula=as.formula(~Site+Condition(PlantIndividual)))
anova(mynmdsSBm,by="terms",permutations = how(nperm=9999))

ordSB <- plot_ordination(datpSB, mynmdsSBm, type="samples", color="Site",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  geom_point(size = 2)+
  #scale_color_manual(values = c("#0047b3", "#99c2ff","#2d862d","#79d279","#b30000","#ff8080"),labels = c("Fresh Native", "Fresh Phragmites","Brackish Native","Brackish Phragmites","Saline Native","Saline Phragmites"),name = "Marsh class/Invasion")+
  #scale_fill_manual(values = c("#0047b3", "#99c2ff","#2d862d","#79d279","#b30000","#ff8080"),labels = c("Fresh Native", "Fresh Phragmites","Brackish Native","Brackish Phragmites","Saline Native","Saline Phragmites"),name = "Marsh class/Invasion")+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(fill=Site),level=.95)


#MM 

datpMM<-datp%>%
  subset_samples(Community.x=="MM")%>%
  filter_taxa(function(x) sum(x>0) >0, prune=T)
unifracMM<-subset_dist(datpMM, unifracp)
MPDdistMM<-subset_dist(datpMM, MPDdist)

#jaccard
mynmdsMMj <- ordinate(datpMM, "CAP",distance(datpMM, method = "jaccard", binary = TRUE),formula=as.formula(~Site+Condition(PlantIndividual)))
anova(mynmdsMMj,by="margin",permutations = how(nperm=9999))

#unifrac
mynmdsMMu <- ordinate(datpMM, "CAP",distance=unifracMM,formula=as.formula(~Site+Condition(PlantIndividual)))
anova(mynmdsMMu,by="margin",permutations = how(nperm=9999))

#bray-curtis
mynmdsMMm <- ordinate(datpMM, "CAP",distance=MPDdistMM,formula=as.formula(~Site+Condition(PlantIndividual)))
anova(mynmdsMMm,by="margin",permutations = how(nperm=9999))

ordMM <- plot_ordination(datpMM, mynmdsMMm, type="samples", color="Site",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(fill=Site),level=.95)


#DM 

datpDM<-datp%>%
  subset_samples(Community.x=="DM")%>%
  filter_taxa(function(x) sum(x>0) >0, prune=T)
unifracDM<-subset_dist(datpDM, unifracp)
MPDdistDM<-subset_dist(datpDM, MPDdist)

#jaccard
mynmdsDMj <- ordinate(datpDM, "CAP",distance(datpDM, method = "jaccard", binary = TRUE),formula=as.formula(~Site))
anova(mynmdsDMj,by="terms",permutations = how(nperm=9999))

#unifrac
mynmdsDMu <- ordinate(datpDM, "CAP",distance=unifracDM,formula=as.formula(~Site))
anova(mynmdsDMu,by="terms",permutations = how(nperm=9999))

#bray-curtis
mynmdsDMm <- ordinate(datpDM, "CAP",distance=MPDdistDM,formula=as.formula(~Site))
anova(mynmdsDMm,by="terms",permutations = how(nperm=9999))

ordDM <- plot_ordination(datpDM, mynmdsDMm, type="samples", color="Site",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(fill=Site),level=.95)

#FF

datpFF<-datp%>%
  subset_samples(Community.x=="FF")%>%
  filter_taxa(function(x) sum(x>0) >0, prune=T)
unifracFF<-subset_dist(datpFF, unifracp)
MPDdistFF<-subset_dist(datpFF, MPDdist)

#jaccard
mynmdsFFj <- ordinate(datpFF, "CAP",distance(datpFF, method = "jaccard", binary = TRUE),formula=as.formula(~Site))
anova(mynmdsFFj,by="terms",permutations = how(nperm=9999))

#unifrac
mynmdsFFu <- ordinate(datpFF, "CAP",distance=unifracFF,formula=as.formula(~Site))
anova(mynmdsFFu,by="terms",permutations = how(nperm=9999))

#bray-curtis
mynmdsFFm <- ordinate(datpFF, "CAP",distance=MPDdistFF,formula=as.formula(~Site))
anova(mynmdsFFm,by="terms",permutations = how(nperm=9999))

ordFF <- plot_ordination(datpFF, mynmdsFFm, type="samples", color="Site",axes=c(1,2))+
  theme_classic()+#  theme(legend.position = "none")
  geom_point(size = 2)+
  stat_ellipse(geom = "polygon", type="t", alpha=0.2, aes(fill=Site),level=.95)

```


# alpha diversity by site

```{r}
div<-dat6%>%
  dplyr::select(Community.x,Site,OTU0:OTU9)%>%
  mutate(Community.x =  factor(Community.x, levels = c("SB", "MM", "DM", "FF"))) %>%
  arrange(Community.x)

data_richness <- estimateR(div[,3:33]) 

# calculate evenness index using vegan package Pielou's measure of species evenness
data_evenness <- diversity(div[,3:33]) / log(specnumber(div[,3:33]))

# calculate Shannon index using vegan package
data_shannon <- diversity(div[,3:33], index = "shannon")

# calculate Shannon index using vegan package
data_simpson <- diversity(div[,3:33], index = "simpson")

# combine all indices in one data table
data_alphadiv <- cbind(div[,1:2], t(data_richness), data_shannon, data_simpson, data_evenness)
colnames(data_alphadiv)[1] <- "Community"
data_alphadiv = data_alphadiv %>% 
  unite(Community_Site, c(,1:2), sep = "_", remove = FALSE)

# remove the unnecessary data/vector
#rm(data_richness, data_evenness, data_shannon, data_simpson)

alpha1 <- ggplot(data_alphadiv, aes(x= Site, y=S.obs,color=Site)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Richness', x= ' ', y= '', tag = "A") +
  geom_point()

alpha2 <- ggplot(data_alphadiv, aes(x=Site, y=S.chao1,color=Site)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Chao1', x= ' ', y= '', tag = "C") +
  geom_point()

alpha3 <- ggplot(data_alphadiv, aes(x=Site, y=data_evenness,color=Site)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Eveness', x= ' ', y= '', tag = "B") +
  geom_point()

alpha4 <- ggplot(data_alphadiv, aes(x=Site, y=data_shannon,color=Site)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Shannon', x= ' ', y= '', tag = "D") +
  geom_point()

alpha5 <- ggplot(data_alphadiv, aes(x=Site, y=data_simpson,color=Site)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Simpson', x= ' ', y= '', tag = "E") +
  geom_point()

# all plots together using the patchwork package
alphaall <- (alpha1 | alpha3) / (alpha2 | alpha4 | alpha5)

```

# alpha diveristy by community

```{r}

alpha1 <- ggplot(data_alphadiv, aes(x= Community, y=S.obs,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Richness', x= ' ', y= '', tag = "A") +
  geom_point()

alpha2 <- ggplot(data_alphadiv, aes(x=Community, y=S.chao1,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Chao1', x= ' ', y= '', tag = "C") +
  geom_point()

alpha3 <- ggplot(data_alphadiv, aes(x=Community, y=data_evenness,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Eveness', x= ' ', y= '', tag = "B") +
  geom_point()

alpha4 <- ggplot(data_alphadiv, aes(x=Community, y=data_shannon,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Shannon', x= ' ', y= '', tag = "D") +
  geom_point()

alpha5 <- ggplot(data_alphadiv, aes(x=Community, y=data_simpson,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Simpson', x= ' ', y= '', tag = "E") +
  geom_point()

# all plots together using the patchwork package
alphaall2 <- (alpha1 | alpha3) / (alpha2 | alpha4 | alpha5)

```

#both site and community

```{r}

alpha1 <- ggplot(data_alphadiv, aes(x= Community, y=S.obs,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Richness', x= ' ', y= '', tag = "A") +
  geom_point()+
  facet_wrap(vars(Site),strip.position = "left", nrow=2)+
  theme(strip.text.x = element_text(size=0))

alpha2 <- ggplot(data_alphadiv, aes(x=Community, y=S.chao1,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Chao1', x= ' ', y= '', tag = "A") +
  geom_point()+
  facet_wrap(vars(Site), nrow=2)+
  theme(strip.text.x = element_text(size=0))

alpha3 <- ggplot(data_alphadiv, aes(x=Community, y=data_evenness,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Eveness', x= ' ', y= '', tag = "B") +
  geom_point() +
  facet_wrap(vars(Site), nrow=2)+
  theme(strip.text.x = element_text(size=0))

alpha4 <- ggplot(data_alphadiv, aes(x=Community, y=data_shannon,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Shannon', x= ' ', y= '', tag = "B") +
  geom_point()+
  facet_wrap(vars(Site), nrow=2)+
  theme(strip.text.x = element_text(size=0))

alpha5 <- ggplot(data_alphadiv, aes(x=Community, y=data_simpson,color=Community)) +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_boxplot() +
  labs(title= 'Simpson', x= ' ', y= '', tag = "C") +
  geom_point()+
  facet_wrap(vars(Site), nrow=2)+
  theme(strip.text.x = element_text(size=0))+
   theme(axis.title.y = element_text(vjust = .5, angle = 0, size = 30))

# all plots together using the patchwork package
alphaall3 <- (alpha2 | alpha4 | alpha5)
alphaall3 <- alphaall3 + 
  facet_grid(Site ~.)+
  theme(strip.text = element_text(size = 12, color = "black"),panel.spacing.y = unit(.5, "cm"))

```

# Stats for alpha diveristy, Shannon

```{r}

#no significnat effect of the sampling site Pr(>F)=0.127
shan_site <- lm(data_shannon ~ Site, data = data_alphadiv,,na.action=na.omit)
anova(shan_site)

shan_com <- lm(data_shannon ~ Community, data = data_alphadiv,na.action=na.omit)
anova(shan_com)

# theres a significant difference in the plant community Pr(>F)=0.0495
shan_com = aov(data_shannon ~ Community, data = data_alphadiv)
summary(shan_com)

# post-hoc test
hsd_test <- TukeyHSD(shan_com) # require the agricolae package  
hsd_res <- HSD.test(shan_com, "Community", group=T)$groups  
show(hsd_res)
#DM and FF are significantly different from eachother, MM and SB are the same, DM is not signifcantly different from MM and SB, FF is not significantly different from MM and SB

options(contrasts=c("contr.helmert","contr.poly"))

shan_sitecom <- summary(aov(data_shannon ~ Site * Community, data = data_alphadiv))
#anova(shan_sitecom)
# there is no significant difference in the site Pr(>F)=0.1050
# would the community be considered significant? Pr(>F)=0.0511
# there is no significant difference in the interaction Pr(>F)=0.3453

shan_comsite <- lm(data_shannon ~ Community_Site, data = data_alphadiv,na.action=na.omit) 
anova(shan_comsite)

shan_comsite <- aov(data_shannon ~ Community_Site, data = data_alphadiv) 
summary(shan_comsite)
hsd_test <- TukeyHSD(shan_comsite)
hsd_res <- HSD.test(shan_comsite, "Community_Site", group = TRUE)$groups  
hsd_res
# DM_P and FF_Q are significantly different

```

# Stats for alpha diveristy, Chao

```{r}

chao_site <- lm(S.chao1 ~ Site, data = data_alphadiv,na.action=na.omit)
anova(chao_site)

chao_com <- lm(S.chao1 ~ Community, data = data_alphadiv,na.action=na.omit)
anova(chao_com)

#no significnat effect of the sampling site Pr(>F)=0.0569??
aov_test= (aov(S.chao1 ~ Site, data = data_alphadiv))
summary (aov_test)

# post-hoc test
hsd_test <- TukeyHSD(aov_test) # require the agricolae package  
hsd_res <- HSD.test(aov_test, "Site", group=T)$groups  
show(hsd_res)
#theres no significant difference between sites

# theres no significant difference in the plant community Pr(>F)=0.148
aov_test = aov(S.chao1 ~ Community, data = data_alphadiv)
summary(aov_test)

# post-hoc test
hsd_test <- TukeyHSD(aov_test) # require the agricolae package  
hsd_res <- HSD.test(aov_test, "Community", group=T)$groups  
show(hsd_res)
#theres no significant difference between any plant communities
#why is DM not different?

summary(aov(S.chao1 ~ Site * Community, data = data_alphadiv))
# there is no significant difference in the site? Pr(>F)=0.0542
# there is no significant difference in the community Pr(>F)=0.1677
# there is no significant difference in the interaction Pr(>F)=0.5625

aov_test <- aov(S.chao1 ~ Community_Site, data = data_alphadiv) 
hsd_test <- TukeyHSD(aov_test)
hsd_res <- HSD.test(aov_test, "Community_Site", group = TRUE)$groups  
hsd_res
# theres no significant difference between any communiy/sites

summary(aov(S.chao1 ~ Community * Site, data = data_alphadiv))

```

# Stats for alpha diveristy, Simpson

```{r}

sim_site <- lm(data_simpson ~ Site, data = data_alphadiv,,na.action=na.omit)
anova(sim_site)

sim_com <- lm(data_simpson ~ Community, data = data_alphadiv,na.action=na.omit)
anova(sim_com)

#no significant effect of the sampling site Pr(>F)=0.287
aov_test=(aov(data_simpson ~ Site, data = data_alphadiv))
summary(aov_test)

# post-hoc test
hsd_test <- TukeyHSD(aov_test) # require the agricolae package  
hsd_res <- HSD.test(aov_test, "Site", group=T)$groups  
show(hsd_res)

# theres no significant difference in the plant community? Pr(>F)=0.0502
aov_test = aov(data_simpson ~ Community, data = data_alphadiv)
summary(aov_test)

# post-hoc test
hsd_test <- TukeyHSD(aov_test) # require the agricolae package  
hsd_res <- HSD.test(aov_test, "Community", group=T)$groups  
show(hsd_res)
#DM and FF are significantly different from eachother, MM and SB are the same, DM is not signifcantly different from MM and SB, FF is not significantly different from MM and SB

summary(aov(data_simpson ~ Site * Community, data = data_alphadiv))
# there is no significant difference in the site Pr(>F)=0.2557
# would the community be considered significant? Pr(>F)=0.0531
# there is no significant difference in the interaction Pr(>F)=0.3117

sim_comsite <- lm(data_simpson ~ Community_Site, data = data_alphadiv,na.action=na.omit)
anova(sim_comsite)

summary(aov(data_simpson ~ Community * Site, data = data_alphadiv))

aov_test <- aov(data_simpson ~ Community_Site, data = data_alphadiv) 
hsd_test <- TukeyHSD(aov_test)
hsd_res <- HSD.test(aov_test, "Community_Site", group = TRUE)$groups  
hsd_res
# DM_P and FF_Q are significantly different

```
# Stats table

```{r}

shan_model <- aov(data_shannon ~ Community * Site,
            data = data_alphadiv)

sstable <- rbind(shan_model)

```

#indexes

```{r}

data_alphadiv_tidy <- 
  data_alphadiv %>%
  mutate(sample_id = rownames(data_alphadiv)) %>%
  gather(key   = alphadiv_index,
         value = obs_values,
         -Community, -Site)

head(data_alphadiv_tidy)


al <- data_alphadiv_tidy %>%  
  filter(alphadiv_index == "S.obs") %>%  
  # fct_relevel() in forecats package to rearrange the sites and months as we want (chronologic) 
  ggplot(., aes(x = Community, y = obs_values,color=Community)) +  
  geom_boxplot(aes(fill = Community)) +  
  geom_point() +  
  facet_grid(. ~ Site) +  
  labs(y = "Richness", x = "") +  
  # x axis label reoriented for better readability  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

al2 <- data_alphadiv_tidy %>%  
  filter(alphadiv_index == "S.chao1") %>%  
  # fct_relevel() in forecats package to rearrange the sites and months as we want (chronologic) 
  ggplot(., aes(x = Community, y = obs_values,color=Community)) +  
  geom_boxplot(aes(fill = Community)) +  
  geom_point() +  
  facet_grid(. ~ Site) +  
  labs(y = "Chao", x = "") +  
  # x axis label reoriented for better readability  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

al3 <- data_alphadiv_tidy %>%  
  filter(alphadiv_index == "data_evenness") %>%  
  # fct_relevel() in forecats package to rearrange the sites and months as we want (chronologic) 
  ggplot(., aes(x = Community, y = obs_values,color=Community)) +  
  geom_boxplot(aes(fill = Community)) +  
  geom_point() +  
  facet_grid(. ~ Site) +  
  labs(y = "Evenness", x = "") +  
  # x axis label reoriented for better readability  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

al4 <- data_alphadiv_tidy %>%  
  filter(alphadiv_index == "data_shannon") %>%  
  # fct_relevel() in forecats package to rearrange the sites and months as we want (chronologic) 
  ggplot(., aes(x = Community, y = obs_values,color=Community)) +  
  geom_boxplot(aes(fill = Community)) +  
  geom_point() +  
  facet_grid(. ~ Site) +  
  labs(y = "Shannon", x = "") +  
  # x axis label reoriented for better readability  
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

al5 <- data_alphadiv_tidy %>%  
  filter(alphadiv_index == "data_simpson") %>%  
  # fct_relevel() in forecats package to rearrange the sites and months as we want (chronologic) 
  ggplot(., aes(x = Community, y = obs_values,color=Community)) +  
  geom_boxplot(aes(fill = Community)) +  
  geom_point() +  
  facet_grid(. ~ Site) +  
  labs(y = "Shannon", x = "") +  
  # x axis label reoriented for better readability  
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```