---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
# Libraries

```{r}

library(plotrix)
library(nlme)
library(cowplot)
library(picante)
library(tidyr)
library(phytools)
library(NLP)
library(Polychrome)
library(forcats)
library(ggtree)

```
#Richness, PD, MPD
should change to referencing dat6 (it is the same data I just added the MPD data to the dat4 dataframe)

``` {r}
options(contrasts=c("contr.helmert","contr.poly"))
options(contrasts=c("contr.treatment","contr.poly"))
options("contrasts")

```

# Calculating richness by plant community

```{r}
dat6DM<-dat6%>%
  filter(Community.x=="DM")%>%
  dplyr::select(OTU0:OTU9)
length(which(colSums(dat6DM)>0)) # 18 taxa in DM

dat6MM<-dat6%>%
  filter(Community.x=="MM")%>%
  dplyr::select(OTU0:OTU9)
length(which(colSums(dat6MM)>0)) # 18 taxa in MM

dat6FF<-dat6%>%
  filter(Community.x=="FF")%>%
  dplyr::select(OTU0:OTU9)
length(which(colSums(dat6FF)>0)) # 15 taxa in FF

dat6SB<-dat6%>%
  filter(Community.x=="SB")%>%
  dplyr::select(OTU0:OTU9)
length(which(colSums(dat6SB)>0)) # 13 taxa in SB

#abundance
rowSums(dat6[,9:42])

```

## Richness

```{r}

richnessmean<-dat6%>%
  group_by(Community.x,Site)%>%
  summarise(mean=mean(SR),se=std.error(SR),count=n())%>%
  ungroup()%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))

#comparing richness in sites by descending moisture 
rm <- ggplot(richnessmean,aes(x=Site,y=mean,color=Site,group=Community.x))+
  labs(x = "",y="Richness") +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth = .5, col="black")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) +
  #scale_color_manual(values = c("gray70","gray50", "gray30"))+
  facet_wrap(vars(Community.x),strip.position = "bottom")
print(rm)


#This is one Emily used for ms
#richness by decending moisture community and sites
#hump-shaped
#I like
rm2 <- ggplot(richnessmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="Richness") +
  theme_classic()+
  theme(line=element_line(linewidth = .3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth = .5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) +
  facet_wrap(vars(Site),strip.position = "bottom")
dev.off()


#Averaging within each Site
richnessmean<-dat4%>%
  # ungroup()%>%
  group_by(Site)%>%
  summarise(mean=mean(SR),se=std.error(SR))

#average richness in each site, increasing in elevation
#Soddie is more rich than saddle, which is expected because saddle is a higher elevation site
rm3 <- ggplot(richnessmean,aes(x=Site,y=mean,color=Site,group=Site))+
  labs(x = "",y="Richness") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth=.5,col="black")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) 

#Averaging within plant community
richnessmean<-dat4%>%
  group_by(Community.x)%>%
  summarise(mean=mean(SR),se=std.error(SR))%>%
  ungroup()%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))

#average richness with descending moisture
#hump-shaped
rm4 <- ggplot(richnessmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="Richness") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth=.5,col="black")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) 

```

##Stats

gls <- fit linear model using generalized least squares

lme <- linear mixed-effects models

``` {r}
m1<-gls(SR~Community.x+Site,data=dat6,na.action=na.omit)
anova(m1,type="marginal")
#statistically different

m1<-lme(SR~Community.x+Site,random=~1|PlantIndividual,data=dat6,na.action=na.omit)
anova(m1,type="marginal")
#statistically different
hist(resid(m1))
boxplot(resid(m1)~dat6$CommunitySitePL)

#with heterogeneous variances, not significant
m1a<-lme(SR~Community.x+Site,random=~1|PlantIndividual,weights=varIdent(form=~1|Site*Community.x),data=dat6,na.action=na.omit)
anova(m1,m1a)
# not statistcially different

```

# Faiths Phylogenetic distance

```{r}

pdmean<-dat6%>%
  group_by(Community.x,Site)%>%
  summarise(mean=mean(PD),se=std.error(PD),count=n())%>%
  ungroup()%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))

#comparing phylogenetic distance in sites by descending moisture
pd <- ggplot(pdmean,aes(x=Site,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="PD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth=.5,col="black")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) +
  #scale_color_manual(values = c("gray70","gray50", "gray30"))+
  facet_wrap(vars(Community.x),strip.position = "bottom")
#dev.off()

#richness by descending moisture community and sites
pd2 <- ggplot(pdmean,aes(x=Community.x,y=mean,color=Site,group=Site))+
  labs(x = "",y="PD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth=.5,col="black")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) +
  #scale_color_manual(values = c("gray70","gray50", "gray30"))+
  facet_wrap(vars(Site),strip.position = "bottom")

#Averaging within each Site
pdmean<-dat4%>%
  # ungroup()%>%
  group_by(Site)%>%
  summarise(mean=mean(PD),se=std.error(PD))

#average phylogenetic distance in each site, increasing in elevation
pd3 <- ggplot(pdmean,aes(x=Site,y=mean,color=Site,group=Site))+
  labs(x = "",y="PD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth=.5,col="black")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) 

#Averaging within community
pdmean<-dat4%>%
  group_by(Community.x)%>%
  summarise(mean=mean(PD),se=std.error(PD))%>%
  ungroup()%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))

#average phylogenetic distance with descending moisture
#hump-shaped
pd4 <- ggplot(pdmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="PD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth=.5,col="black")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) 
```

## Stats
``` {r}
m1<-gls(PD~Community.x+Site,data=dat6,na.action=na.omit)
#m1<-gls(mpd.obs.z.weighted~Site,data=dat6,na.action=na.omit)
anova(m1,type="marginal")

```

# MPD

an MPD that is > 0 is overdispersion, and MPD < 0 is phylogenetic clustering
mpd.obs.z is what we want it compares the observed to the randomized data, if > 0 overdispersion, if < 0 clustered

``` {r}

mpdmean<-dat6%>%
  group_by(Site,Community.x)%>%
  filter(is.na(mpd.obs.z.weighted)==F)%>%
  summarise(mean=mean(mpd.obs.z.weighted,na.rm=T),se=std.error(mpd.obs.z.weighted),n=n())%>%
  ungroup()%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))
mpdmean

#This is one emily used for ms
#mean pairwise distance by descending moisture community and sites
mpd <- ggplot(mpdmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="MPD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) +
  facet_wrap(vars(Site),strip.position = "bottom")
dev.off()

#comparing mean pairwise distance in sites by descending moisture
mpd2 <- ggplot(mpdmean,aes(x=Site,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="MPD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth=.5,col="black")+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) +
  facet_wrap(~Community.x)#,strip.position = "bottom")

#adding line element
mpd3 <- ggplot(mpdmean,aes(x=Community.x,y=mean,color=Community.x,group=Site))+
  labs(x = "",y="MPD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(.5,"cm"),strip.placement = "outside")+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) +
  facet_wrap(~Site)#,strip.position = "bottom")

#with plant individual
mpdmean<-dat6%>%
  group_by(Site,Community.x,PlantIndividual)%>%
  filter(is.na(mpd.obs.z.weighted)==F)%>%
  summarise(mean=mean(mpd.obs.z.weighted,na.rm=T),se=std.error(mpd.obs.z.weighted),n=n())%>%
  ungroup()%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))

mpd4 <- ggplot(mpdmean,aes(x=Site,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="MPD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
#  geom_line(stat = "identity", position = "identity",size=.5,col="black")+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) +
  facet_wrap(~Community.x)#,strip.position = "bottom")

options(contrasts=c("contr.helmert","contr.poly"))
options(contrasts=c("contr.treatment","contr.poly"))

```

## Stats

```{r}

# m1<-gls(mpd.obs.z.weighted~HostPlant+Site,data=dat6,na.action=na.omit)
# anova(m1,type="marginal")
 
# m2<-gls(mpd.obs.z.weighted~HostPlant*Site,data=phragspartina,na.action=na.omit)
# anova(m2,type="marginal")

m1<-lme(mpd.obs.z.weighted~Community.x+Site,random=~1|PlantIndividual,data=dat6,na.action=na.omit)
# m2<-lme(mpd.obs.z.weighted~HostPlant+Site,random=~1|Year,weights=varIdent(form=~1|Site),data=dat6,na.action=na.omit)
# m3<-lme(mpd.obs.z.weighted~HostPlant+Site,random=~1|Year,weights=varIdent(form=~1|HostPlant),data=dat6,na.action=na.omit)
# m4<-lme(mpd.obs.z.weighted~HostPlant+Site,random=~1|Year,weights=varIdent(form=~1|HostPlantSite),data=dat6,na.action=na.omit)
# anova(m1,m2,m3,m4)
anova(m1,type="marginal")
hist(resid(m1))
plot(fitted(m1),resid(m1))


#remove the space in HostPlantSite and make it a factor
#dat6$HostPlantSite<-gsub("\\s+", "", dat6$HostPlantSite)
#dat6$HostPlantSite<-factor(dat6$HostPlantSite)

m2<-lme(mpd.obs.z.weighted~HostPlantSite,random=~1|Year,data=dat6,na.action=na.omit)#,weights=varIdent(form=~1|HostPlantSite)
m2<-gls(mpd.obs.z.weighted~HostPlantSite,data=dat6,na.action=na.omit)#,weights=varIdent(form=~1|HostPlantSite)

#this does not work, it gives the wrong means
#summary(glht(m2, linfct = mcp(HostPlantSite=c("Phragmitesaustralis_TurtleCove=0","Sagittarialancifolia_TurtleCove=0","Spartinapatens_TurtleCove=0","Phragmitesaustralis_CERF=0","Spartinaalterniflora_CERF=0","Spartinapatens_CERF=0","Juncusroemerianus_LUMCON=0","Phragmitesaustralis_LUMCON=0","Spartinaalterniflora_LUMCON=0","Spartinapatens_LUMCON=0"))))

m2em<-as.data.frame(summary(emmeans(m2,~HostPlantSite)))
m2.r<-ref_grid(m2)
m2.s<-emmeans(m2.r,"HostPlantSite")
test(m2.s,adjust="fdr")#dunnett (what glht uses) or fdr


m2<-lme(mpd.obs.z.weighted~HostPlant*Site,random=~1|Year,data=phragspartina,na.action=na.omit)
anova(m2,type="marginal")

#tyring heterogeneou variances, not significant
#m2a<-lme(mpd.obs.z.weighted~HostPlant*Site,random=~1|Year,weights=varIdent(form=~1|HostPlant*Site),data=phragspartina,na.action=na.omit)
#anova(m2,m2a)

# m2<-lme(mpd.obs.z.weighted~Site,random=~1|HostPlant,data=dat6,na.action=na.omit)
# anova(m2)

```

# Plot for mdp and richness together

```{r}

richnessmean<-dat6%>%
  group_by(Community.x,Site)%>%
  summarise(mean=mean(SR),se=std.error(SR),count=n())%>%
  ungroup()%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))

richfig<-ggplot(richnessmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="Richness") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) +
  facet_wrap(vars(Site),strip.position = "bottom")

mpdmean<-dat6%>%
  group_by(Site,Community.x)%>%
  filter(is.na(mpd.obs.z.weighted)==F)%>%
  summarise(mean=mean(mpd.obs.z.weighted,na.rm=T),se=std.error(mpd.obs.z.weighted),n=n())%>%
  ungroup()%>%
  mutate(Community.x = fct_relevel(Community.x,"SB", "MM", "DM", "FF"))

mpdfig<-ggplot(mpdmean,aes(x=Community.x,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="MPD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=12),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",strip.placement = "outside",panel.spacing=unit(0,"cm"),axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),panel.background = element_rect(fill = NA, color = "gray50"))+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=2.75)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.35,size=1) +
  facet_wrap(vars(Site),strip.position = "bottom")


#pdf("/Users/farrer/Dropbox/EmilyComputerBackup/Documents/LAmarsh/Culturing/Manuscripts/richnessmpd.pdf")
plot_grid(richfig, mpdfig, nrow = 2)
dev.off()

```

## MPD trials

below are the trials that I did for individual (abundance weighted vs not and grouped by species x site, site, and species)

MPD by plant individual 
notes on results of unweighted vs weighted. the overall pattern is very similar, but the weighted results tend to have slightly smaller error bars so that some (junroe) might be significantly positive. However, it probably makes the most sense to use unweighted because (based on the labeling file in google drive) it sounds like they only isolated one "morphotype" per plate (of 5 root pieces) therefore it is unlikely to get an abundance >2 (there were two plates of 5 roots each for each sample).

```{r}

phydist <- cophenetic(cleanedtree_v2)
ses.mpd.result.ind <- ses.mpd(dat.comm, phydist, null.model="taxa.labels",abundance.weighted=FALSE, runs=999) #takes 5 min with 999
ses.mpd.result.ind$CommunitySitePL<-rownames(ses.mpd.result.ind)
ses.mpd.result.ind

mpdmean<-ses.mpd.result.ind%>%
  full_join(dat4)%>%
  group_by(Site,Community.x)%>%
  filter(is.na(mpd.obs.z)==F)%>%
  summarise(mean=mean(mpd.obs.z,na.rm=T),se=std.error(mpd.obs.z),n=n())%>%
  ungroup()
mpdmean

ses.mpd.result.ind.abun <- ses.mpd(dat.comm, phydist, null.model="taxa.labels",abundance.weighted=T, runs=999) #takes 5 min with 999
ses.mpd.result.ind.abun$CommunitySitePL<-rownames(ses.mpd.result.ind.abun)
ses.mpd.result.ind.abun

mpdmean<-ses.mpd.result.ind.abun%>%
  full_join(dat4)%>%
  group_by(Site,Community.x)%>%
  filter(is.na(mpd.obs.z)==F)%>%
  summarise(mean=mean(mpd.obs.z,na.rm=T),se=std.error(mpd.obs.z),n=n())%>%
  ungroup()
mpdmean

trial <- ggplot(mpdmean,aes(x=Site,y=mean,color=Community.x,group=Community.x))+
  labs(x = "",y="MPD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(0,"cm"),strip.placement = "outside")+
  geom_line(stat = "identity", position = "identity",linewidth=.5,col="black")+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) +
  facet_wrap(~Community.x)#,strip.position = "bottom")

trial2 <- ggplot(mpdmean,aes(x=Community.x,y=mean,color=Community.x,group=Site))+
  labs(x = "",y="MPD") +
  theme_classic()+
  theme(line=element_line(linewidth=.3),text=element_text(size=10),strip.background = element_rect(colour="white", fill="white"),axis.line=element_line(color="gray30",linewidth=.5),legend.position = "none",panel.spacing=unit(.5,"cm"),strip.placement = "outside")+
  #geom_line(stat = "identity", position = "identity",size=.5,col="black")+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=1.8)+
  geom_errorbar(aes(ymax = mean+se, ymin=mean-se),width=.25,size=.5) +
  facet_wrap(~Site)#,strip.position = "bottom")

```

## Stats

``` {r}

dm1<-gls(mpd.obs.z~HostPlant+Site,data=dat6,na.action=na.omit)
m1<-gls(mpd.obs.z~Site,data=dat6,na.action=na.omit)
anova(m1)

m2<-lme(mpd.obs.z~Site,random=~1|HostPlant,data=dat6,na.action=na.omit)
anova(m2)

```

#Summing by community and site
Phrag TC is sig, Phrag LUMCON nearly sig; alterniflora CERF nearly sig, alternaflora LUMCON sig; patens CERF nearly sig

```{r}
phydist <- cophenetic(cleanedtree_v2)

dat.comm.sum<-dat6%>%
  group_by(Community.x,Site)%>%
  summarise(across(OTU0:OTU9,sum))%>%
  unite(CommunitySite,Community.x,Site)
dat.comm.sum$CommuitySite<-apply(as.matrix(dat.comm.sum$CommunitySite),1,function(x){gsub(" ", "", x)})
dat.comm.sum<-data.frame(dat.comm.sum)
row.names(dat.comm.sum)<-dat.comm.sum$CommunitySite
dat.comm.sum$CommunitySite<-NULL

#ses.mntd.result <- ses.mntd(dat.comm.sum, phydist, null.model="taxa.labels", abundance.weighted=FALSE, runs=999)
#ses.mntd.result

ses.mpd.result.sum <- ses.mpd(dat.comm.sum[,1:34], phydist, null.model="taxa.labels", abundance.weighted=F, runs=999)
ses.mpd.result.sum


#Summing by community
#spartina alterniflora nearly sig
dat.comm.sum.DM<-dat6%>%
  group_by(Community.x)%>%
  summarise(across(OTU0:OTU9,sum))
dat.comm.sum.DM$Community.x<-apply(as.matrix(dat.comm.sum.DM$Community.x),1,function(x){gsub(" ", "", x)})
dat.comm.sum.DM<-data.frame(dat.comm.sum.DM)
row.names(dat.comm.sum.DM)<-dat.comm.sum.DM$Community.x
dat.comm.sum.DM$Community.x<-NULL

ses.mpd.result.sum.DM <- ses.mpd(dat.comm.sum.DM, phydist, null.model="taxa.labels",abundance.weighted=FALSE, runs=999)
ses.mpd.result.sum.DM



#Summing by site
#no significance
dat.comm.sum.site<-dat6%>%
  group_by(Site)%>%
  summarise(across(OTU0:OTU9,sum))
dat.comm.sum.site$Site<-apply(as.matrix(dat.comm.sum.site$Site),1,function(x){gsub(" ", "", x)})
dat.comm.sum.site<-data.frame(dat.comm.sum.site)
row.names(dat.comm.sum.site)<-dat.comm.sum.site$Site
dat.comm.sum.site$Site<-NULL

ses.mpd.result.sum.site <- ses.mpd(dat.comm.sum.site, phydist, null.model="taxa.labels",abundance.weighted=F, runs=999)
ses.mpd.result.sum.site

```

# Tree plotting

```{r}
# par(mfrow=c(2,2))
# for (i in names(traits)) {
#   plot(phy, show.tip.label=FALSE, main=i)
#   tiplabels(pch=22, col=traits[,i]+1, bg=traits[,i]+1, cex=1.5)
# }

dat.comm.sum.DMt<-as.data.frame(t(dat.comm.sum.DM))
dat.comm.sumt<-as.data.frame(t(dat.comm.sum))

plot(cleanedtree_v2, show.tip.label=FALSE)
colort<-ifelse(dat.comm.sumt$DM >0,2,1)
tiplabels(pch=22, col=colort, bg=colort, cex=1.5)

plot(cleanedtree_v2, show.tip.label=T)

```

# Tree heatmap

this is made with absolute abundances, but would relative abundances be better to use?

```{r}

labels <- guilds%>%
  dplyr::select(OTU,Genus,Species,trophicMode)
labels$Genus <- stringr::str_replace(labels$Genus, 'g__', '')
labels$Species <- stringr::str_replace(labels$Species, 's__', '')
labels <- labels[-c(3),]
labels <- labels%>%
  unite(GenusSpecies, Genus, Species)
labels$OTUGS <- paste(labels$OTU, labels$GenusSpecies, sep="_")

matrix <- dat.comm.sumt[1:34,]
matrix2 <- apply(matrix,2,trimws)
heatmat <- matrix2

for (i in 1:nrow(matrix2)){
  for (j in 1:ncol(matrix2)){
  if (matrix2[i,j]==0){
    heatmat[i,j]="a"
    } else if(matrix2[i,j]==1 || matrix2[i,j]==2){
    heatmat[i,j]="b"
    } else if(matrix2[i,j]==3 || matrix2[i,j]==4) {
    heatmat[i,j]="c"
    } else if(matrix2[i,j]==5 || matrix2[i,j]==6) {
    heatmat[i,j]="d"
    } else if(matrix2[i,j]==7 || matrix2[i,j]==8) {
    heatmat[i,j]="e"
    } else if(matrix2[i,j]==9 || matrix2[i,j]==10) {
    heatmat[i,j]="f"
    } else if(matrix2[i,j]==11 || matrix2[i,j]==12) {
    heatmat[i,j]="g"
    } else if(matrix2[i,j]==13 || matrix2[i,j]==14) {
    heatmat[i,j]="h"
    } else if(matrix2[i,j]==15 || matrix2[i,j]==16) {
    heatmat[i,j]="i"
    } 
  }
}

matrix3 <- matrix2 %>%
  data.frame()%>%
  dplyr::select(SB_P,SB_Q,MM_P,MM_Q,DM_P,DM_Q,FF_P,FF_Q)
rownames(matrix3) <- labels[[4]][match(rownames(matrix3), labels[[1]])]

write.csv(matrix3,"C:/Users/Kacey/Documents/Tulane/Lab/Culture/Geum roots/Treeheatmat.csv")
tree.heat2 <- read.csv("C:/Users/Kacey/Documents/Tulane/Lab/Culture/Geum roots/Treeheatmat.csv", row.names=1, stringsAsFactors = TRUE)

cleanedtree_v2 <- read.tree("C:/Users/Kacey/Documents/Tulane/Lab/Culture/Geum roots/Data/cleanedtree_V2.nwk")
cleanedtree_v2$tip.label <- geumroot[[16]][match(cleanedtree_v2$tip.label, geumroot[[1]])]
cleanedtree_v2$tip.label <- labels[[4]][match(cleanedtree_v2$tip.label, labels[[1]])]

p <- ggtree(cleanedtree_v2) + 
    geom_tiplab(size=2, align=TRUE, linesize=.5)
gheatmap(p, tree.heat2, offset=1, width=0.5,font.size = 2, 
  colnames_angle=-45,hjust=0) +       
  scale_x_ggtree() + 
  scale_y_continuous(expand=c(0, 2)) + 
  scale_fill_gradient(low = "white", high = "steelblue", name = "Abundance")
  #scale_fill_manual(values=c("#fff7fb", "#ece2f0", "#d0d1e6","#a6bddb","#67a9cf","#3690c0","#02818a","#016c59","#014636"), name="Abundance")

```


# Tree with absent/present

``` {r}

matrix <- dat.comm.sumt[1:34,]
matrix2 <- apply(matrix,2,trimws)
matrix3 <- ifelse(matrix2 == 0, "Absent","Present")
matrix4 <- matrix3 %>%
  data.frame()%>%
  dplyr::select(SB_P,SB_Q,MM_P,MM_Q,DM_P,DM_Q,FF_P,FF_Q)
rownames(matrix4) <- labels[[4]][match(rownames(matrix4), labels[[1]])]
rownames(labels) <- labels[[4]]
mat <- merge(matrix4,labels,by=0)
mat <- mat%>%
  dplyr::select(Row.names,SB_P,SB_Q,MM_P,MM_Q,DM_P,DM_Q,FF_P,FF_Q)

write.csv(mat,"C:/Users/Kacey/Documents/Tulane/Lab/Culture/Geum roots/Treemat.csv")
tree.data <- read.csv("C:/Users/Kacey/Documents/Tulane/Lab/Culture/Geum roots/Treemat.csv", row.names=2, stringsAsFactors = TRUE)
tree.data$X <- NULL

cleanedtree_v2 <- read.tree("C:/Users/Kacey/Documents/Tulane/Lab/Culture/Geum roots/Data/cleanedtree_V2.nwk")
cleanedtree_v2$tip.label <- geumroot[[16]][match(cleanedtree_v2$tip.label, geumroot[[1]])]
cleanedtree_v2$tip.label <- labels[[4]][match(cleanedtree_v2$tip.label, labels[[1]])]


tree <- plotTree.datamatrix(cleanedtree_v2,tree.data,fsize=0.5,palettes=c("YlOrRd","PuBuGn"),yexp=1.12,xexp=2)
leg <- legend(x="topright",names(tree$colors$DM_P),cex=0.7,pch=22,pt.bg=tree$colors$DM_P,pt.cex=1.5,bty="n",title="Soddie")
#leg2 <- legend(x="bottomright",names(tree$colors$DM_Q),cex=0.7,pch=22,pt.bg=tree$colors$DM_Q,pt.cex=1.5,bty="n",title="Saddle")
leg2 <- legend(x=(leg$rect$left), y=(leg$rect$top-leg$rect$h),names(tree$colors$DM_Q),cex=0.7,pch=22,pt.bg=tree$colors$DM_Q,pt.cex=1.5,bty="n",title="Saddle")

```